---
title: Syllabus
slug: syllabus
citeproc: true
output:
  blogdown::html_page:
    toc: true
    fig_caption: false
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
```
# Objectives

Psychological methods keep evolving: psychology researchers constantly adopt new statistical methods, computational tools, and research practices. This course introduces the latest advances in research methods in psychological science through a series of discussions, tutorials, and seminars. Lectures are generally given by a guest speaker who introduces methodological and statistical issues relevant to psychology research. Tutorials provide students with the necessary skills to build reproducible and transparent research programs. For instance, students learn how to use R, RMarkdown and Git/GitHub, or how to preregister their studies. Finally, students take part in seminars, in which they discuss timely topics in psychological methods (e.g., reproducibility, transparency, pre-registration).

\vspace{.75cm}

# Prerequisites and Audience

This is a graduate-level course. Any graduate students in psychology can attend.

\vspace{.75cm}

# Class format

We will meet once a week throughout the semester. The format will depend on the topic and the objective of the class. In this course, students will attend: i) discussions, ii) seminars, and iii) tutorials.

-   **Discussions.** Students will participate in discussions on various research issues. We will have several articles to discuss. On these days you must prepare 2-4 discussion questions based on the journal article assigned for the date. These questions should highlight important points of the reading as well as demonstrate understanding of the methodology and primary findings of the articles. Discussion questions may address relevance of the article's findings or conclusions to your own practice or future work, and/or connections to other readings in the course or readings from other courses. You will be asked to lead class discussion utilizing these questions. Selected students will turn in a written copy of their questions for grading at the end of the class discussion. Grade on this assignment is based on the content of the questions as well as the discussion lead in class.
-   **Guest Seminars.** Students will attend a series of lectures during the semester. Lectures may introduce a recent methodological contribution or discuss a controversial and easily overlooked issue regarding the application or interpretation of statistics. Lectures will be given by guest speakers who are expert in the topic.
-   **Tutorials.** Students will learn skills to build reproducible and transparent research programs. These tutorials may teach students how to preregister their studies, run power analyses, and organize their code with Notebooks). Tutorials may be given by guest speakers who are expert in the topic.

\vspace{.75cm}

# Readings

Much of the material needed for the course will be available on Canvas. I will also post it on the course OSF page: <https://osf.io/qh9rb/>.


\vspace{.75cm}

# Grading

# Assignments and Grades

## Discussion Reflections

 We have a several guest lectures over the course of the semester. You will get points for attending these talks and submitting a reflection for each talk/presentation (500-1000 words). Reflections will be due on the Friday by 4:00 P.M after the talk.These must be submitted via Canvas. The purpose of the response is to get you thinking about the content at a higher-level.


    ```{html}
    <style type="text/css">
    .tg  {border-collapse:collapse;border-spacing:0;}
    .tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
      overflow:hidden;padding:10px 5px;word-break:normal;}
    .tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
      font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
    .tg .tg-7zrl{text-align:left;vertical-align:bottom}
    .tg .tg-0lax{text-align:left;vertical-align:top}
    </style>
    ```
    +-----------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+
    | Great                                                                                                                                   | Proficient                                                                                           | Developing                                                                                                          | Unsatisfactory                                                                                                 |
    +=========================================================================================================================================+======================================================================================================+=====================================================================================================================+================================================================================================================+
    | 3                                                                                                                                       | 2                                                                                                    | 1                                                                                                                   | 0                                                                                                              |
    +-----------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+
    | The response is well developed. It indicates\                                                                                           | The response is\                                                                                     | The response is not\                                                                                                | The response was not\                                                                                          |
    | that the presentation and the material was\                                                                                             | adequate. There is\                                                                                  | adequate. There may be\                                                                                             | submitted properly to\                                                                                         |
    | understood. It\                                                                                                                         | evidence that the\                                                                                   | little evidence that the\                                                                                           | Canvas by the deadline.                                                                                        |
    | expands on, elaborates,\                                                                                                                | material was read and\                                                                               | material was read or\                                                                                               |                                                                                                                |
    | or offers a unique\                                                                                                                     | understood. Elaboration\                                                                             | understood. There is no\                                                                                            |                                                                                                                |
    | insight on the material.                                                                                                                | or unique insights may be less developed.                                                            | elaboration                                                                                                         |                                                                                                                |
    +-----------------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+

##  Tutorial

For your final project you will create a tutorial about how to something in R.The final project gives you a chance to pursue any topic in the R universe and learn more about it. For example, you could choose to write a tutorial on any R package or how to perform a statistical analysis.

There is no final exam. This project is your final exam.

## Assignment Grades

```{r assignments-grades, include=FALSE}
assignments <- tribble(
  ~Points,  ~Assignment,
  25      , "Participation",
  5*9, "Quizzes [9 x 5 pts.]",
  7 * 35  , "Lab Assignments [7 x 35 pts.]",
  85     , "Midterm",
  100, "Final Meta-analysis Project [Presentation = 50; Writeup = 50]",
) %>%
  mutate(Percent = Points / sum(Points),
         Percent = scales::percent(Percent)) 
grading <- tribble(
  ~Grade, ~Range,
  "A",  "90–100%",
  "B",  "80–89%",
   "C",  "70-79%", 
  "D",  "60-69%"
)
```

```{r show-assignments-table, echo=FALSE, results="asis"}
assignments_total <- tibble(Assignment = "Total",
                            Points = sum(assignments$Points),
                            Percent = NA)
bind_rows(assignments, assignments_total) %>% 
  select(Assignment, Percent, Points) %>% 
  pandoc.table(justify = "lrr", missing = "")
```

Students' grade will be based on reflection papers and participation in discussion.
