---
title: Syllabus
date:  "`r Sys.Date()`"
slug: syllabus
citeproc: true
output:
  blogdown::html_page:
    toc: true
    fig_caption: false
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
```


# Objectives

Psychological methods keep evolving: psychology researchers constantly adopt new statistical methods, computational tools, and research practices. This course introduces the latest advances in research methods in psychological science through a series of discussions, tutorials, and seminars. Lectures are generally given by a guest speaker who introduces methodological and statistical issues relevant to psychology research. Tutorials provide students with the necessary skills to build reproducible and transparent research programs. For instance, students learn how to use R, RMarkdown and Git/GitHub, or how to preregister their studies. Finally, students take part in seminars, in which they discuss timely topics in psychological methods (e.g., reproducibility, transparency, pre-registration).

\vspace{.75cm}

# Prerequisites and Audience

This is a graduate-level course. Any graduate students in psychology can attend.

\vspace{.75cm}

# Class Format

We will meet once a week throughout the semester. The format will depend on the topic and the objective of the class. In this course, students will attend: i) discussions, ii) seminars, and iii) tutorials.

-   **Discussions.** Students will participate in discussions on various research issues. We will have several articles to discuss. 
-   **Guest Seminars.** Students will attend a series of lectures during the semester. Lectures may introduce a recent methodological contribution or discuss a controversial and easily overlooked issue regarding the application or interpretation of statistics. Lectures will be given by guest speakers who are expert in the topic.
-   **Tutorials.** Students will learn skills to build reproducible and transparent research programs. These tutorials may teach students how to preregister their studies, run power analyses, and organize their code with Notebooks). Tutorials may be given by guest speakers who are expert in the topic.

\vspace{.75cm}

# Readings

Much of the material needed for the course will be available on Canvas. I will also post it on the course website: https://psy505.netlify.app/

\vspace{.75cm}

# Grading

# Assignments

## Speaker Reflections (30%)

We have several guest lectures over the course of the semester. You will get points for attending these talks and submitting a reflection for each talk (~500-1000 words). Reflections will be due on the Friday by 4:00 P.M after the talk.These must be submitted via Canvas. The purpose of the response is to get you thinking about the content. These will be graded as ✅ 
or ⛔
 
## Tutorial Assignments (30%)

On tutorial days, there will be an assignment applying what was learned during the tutorial. These will be graded as ✅ 
or ⛔


## Leading Discussion  (10%)

Once during the semester you (possibly in a pair) will be
responsible for leading discussions with that week’s class guest or reading. Your job will be easier if everyone jumps in and asks questions, but if the discussion is lagging, you’ll jump in with some prepared questions for the speaker.

## Write Your Own Tutorial (30%)

For your final project you will create a tutorial about how to do something in R.The final project gives you a chance to pursue any topic in the R universe and learn more about it. For example, you could choose to write a tutorial on any R package or how to perform a statistical analysis.

There is no final exam. This project is your final exam.

# Grades

```{r assignments-grades, include=FALSE}
assignments <- tribble(
  ~Points,  ~Assignment,
  5*6      , "Speaker Reflections",
  30, "Tutorial Assignments",
  10, "Dicussions", 
  30, "Tutorial",
) %>%
  mutate(Percent = Points / sum(Points),
         Percent = scales::percent(Percent)) 
grading <- tribble(
  ~Grade, ~Range,
  "A",  "90–100%",
  "B",  "80–89%",
   "C",  "70-79%", 
  "D",  "60-69%"
)
```

```{r show-assignments-table, echo=FALSE, results="asis"}
assignments_total <- tibble(Assignment = "Total",
                            Points = sum(assignments$Points),
                            Percent = NA)
bind_rows(assignments, assignments_total) %>% 
  select(Assignment, Percent, Points) %>% 
  pandoc.table(justify = "lrr", missing = "")
```

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lc", 
               col.names = c("Grade", "Range"))
```